### 2017-09-19 icde/sec-exp.tex

\etitle{Exp-4.3}.
To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01. Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency. The results are reported in Fig.~\ref{exp-ab}, where the parameters selected earlier and their corresponding \PairAcc are marked with $*$.

>>>>

\etitle{Exp-4.3}.
To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01. Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency. The results are reported in Fig.~\ref{exp-ab}, where the parameters $\alpha$ and $\beta$ are set by default (used earlier) the corresponding values of $\alpha$-axis and $\beta$-axis, respectively, of the \PairAcc marked with $\star$.
